---
title: "R Notebook"
output: html_notebook
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
library(tidyverse)
library(tidyquant)
library(highcharter)
library(timetk)
library(tibbletime)

load("book-data.Rdata")
```

- different ways of making data available to your audience
- readability is part of reproducibility; 
- conversant if not fluent
- the scalpel example
- Technology: Notebooks and Shiny
- stacked rolling histograms - I don't like them, maybe you do, I prefer lines, or lines with total
- probability will outperform 
- up month or down month based on: previous 6 months, or previous 6 january's
- how about a quick strategy
- VaR monte carlo *good way to add more*



```{r}
portfolio_var_gaussian_xts <- VaR(portfolio_returns_xts_rebalanced_monthly, method = "gaussian")

portfolio_var_gaussian_xts
```

```{r}
portfolio_var_historical_xts <- VaR(portfolio_returns_xts_rebalanced_monthly, method = "historical")

portfolio_var_historical_xts
```

```{r}
portfolio_var_modified_xts <- VaR(portfolio_returns_xts_rebalanced_monthly, method = "modified")

portfolio_var_modified_xts
```

```{r}
kurt <- kurtosis(portfolio_returns_xts_rebalanced_monthly)
skew <- skewness(portfolio_returns_xts_rebalanced_monthly)
mean <- mean(portfolio_returns_xts_rebalanced_monthly)
sd <- sd(portfolio_returns_xts_rebalanced_monthly)
z <- -1.64
mean + (z + 
          (
            (skew*(z^2 - 1))/6 + 
            (kurt*(z^3 - (3*z)))/24 - 
            (((skew ^2)*(2 * z^3 - (5 * z))))/36
          )
        /sd)

```

$$z_{cf}=q_{c}+frac{(q_{c}^{2}-1)S}{6}+frac{(q_{c}^{3}-3q_{c})K}{24}-frac{(2q_{c}^{3}-5q_{c})S^{2}}{36}$$

```{r}
zcf <- z + 
          (
            (skew*(z^2 - 1))/6 + 
            (kurt*(z^3 - (3*z)))/24 - 
            (((skew ^ 2)*(2 * z^3 - (5 * z))))/36
          )

mean - (zcf * sd)
```


$$modVaR =bar{R} - σ cdot z_{cf}$$
```{r}
probs <- c(.005, .025, .25, .5, .75, .975, .995)
dist_log_returns <- 
  
  
  portfolio_returns_dplyr_byhand$returns %>% 
    quantile(probs = .95)

portfolio_var_gaussian_xts <- VaR(portfolio_returns_xts_rebalanced_monthly, method = "gaussian")

portfolio_var_gaussian_xts

```

```{r}
# equivalent
mean(portfolio_returns_xts_rebalanced_monthly) + ((-1.64485) * sd(portfolio_returns_xts_rebalanced_monthly))

mu.hat = mean(portfolio_returns_tq_rebalanced_monthly$returns)
sigma.hat = sd(portfolio_returns_tq_rebalanced_monthly$returns)
mu.hat + sigma.hat*qnorm(0.05)
```


```{r}
ES.fun = function(x, alpha=0.05) {
  qhat = quantile(x, probs = alpha)
  mean(x[x <= qhat])
}
ES.fun(portfolio_returns_tq_rebalanced_monthly$returns)
```



```{r}
portfolio_returns_tq_rebalanced_monthly %>%
    tq_performance(Ra = returns, Rb = NULL, performance_fun = VaR)
```

```{r}
# Assuming it's normal
VaR_guassian_byhand <-
  qnorm(.05, 
        mean(portfolio_returns_tq_rebalanced_monthly$returns), 
        sd(portfolio_returns_tq_rebalanced_monthly$returns))


VaR_guassian_tq <- 
  portfolio_returns_tq_rebalanced_monthly %>%
  tq_performance(Ra = returns,
                 Rb = NULL,
                 performance_fun = VaR, 
                 p = .95, 
                 method = "gaussian") %>% 
  rename(VaR_tq = VaR)
  
VaR_guassian_xts <- 
  
  VaR(portfolio_returns_xts_rebalanced_monthly,
                        method = "gaussian", 
                        mu = mean(portfolio_returns_xts_rebalanced_monthly), 
      sigma = var(portfolio_returns_xts_rebalanced_monthly)) 


VaR_guassian_byhand
VaR_guassian_xts
VaR_guassian_tq
```

```{r}
mean(portfolio_returns_tq_rebalanced_monthly$returns) + sd(portfolio_returns_tq_rebalanced_monthly$returns)*qnorm(0.05)
```


```{r}


Var_historical <- quantile(portfolio_returns_xts_rebalanced_monthly, probs = .05)

VaR_historical_tq <- 
  portfolio_returns_tq_rebalanced_monthly %>%
  tq_performance(Ra = returns,
                 Rb = NULL,
                 performance_fun = VaR, 
                 p = .95, 
                 method = "historical") %>% 
  rename(VaR_tq = VaR)
  
VaR_historical_xts <- 
  
  VaR(portfolio_returns_xts_rebalanced_monthly,
                        method = "historical")
```

```{r}
portfolio_returns_tq_rebalanced_monthly %>% 
  ggplot(aes(returns)) +
  geom_histogram(binwidth = .003) +
 geom_vline(xintercept = (-1.644 * sd(portfolio_returns_tq_rebalanced_monthly$returns), color = "blue") +
  geom_vline(xintercept = -.0428, color = "red") +
  geom_vline(xintercept = mean(portfolio_returns_tq_rebalanced_monthly$returns, color = "purple")) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 20))
```

